---
output:
  html_document:
    keep_md: yes
    toc: no
    self_contained: no
---

## CSCI

#### *Raphael Mazor, raphaelm@sccwrp.org, Marcus W. Beck, marcusb@sccwrp.org, Mark W Engeln*

R package materials to calculate the California Stream Condition Index (CSCI) based on O/E and pMMI scores using benthic macroinvertebrates.

### Installation

Install the package as follows:

```{r, eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('SCCWRP/CSCI')
library(CSCI)
```

### Citation

Please cite the package as follows:

Mazor, MD, Rehn, AC, Ode, PR, Engeln, M, Schiff, KC, Stein, ED, Gillett, DJ, Herbst, DB, Hawkins, CP. 2016. Bioassessment in complex environments: Designing an index for consistent meaning in different settings. Freshwater Science 35(1): 249-271.

### Usage

The core function is `CSCI` which requires taxonomic and site level data.
```{r, echo = F, warning = F, message = F}
devtools::load_all()
```
```{r}
#A list of two data frames: bugs and stations
data(bugs_stations) 

# run the estimator
results <- CSCI(bugs = bugs_stations[[1]], stations = bugs_stations[[2]])

#see all the components of the report
ls(results)

 #see the core report
results$core
```

